{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-29 paper.tex
More on complexity analysis

>>>>

\subsection{Time and space complexity analysis}

\uwds is fundamentally about distributing two datastructures: a scene graph
(with nodes representing spatial entities) and a timeline (where events are
stored as a flat list). Typical time and space complexities arise from these
datastructures. In typical usage scenarios (where the number of nodes or events
remain relatively small), the computational load to manipulate these
datastructures is however dominated by the actual processings performed by the
clients with the data.

More interesting is the time complexity of distributing changes across an \uwds
network. With $n$ the number of worlds and $m$ the number of operators in a
network $\mathcal{N}$, the worst-case (when every world is a parameter of every
operator) time complexity of creating or updating a node and propagating the
change across the network is $O(n \times m)$ (this effectively corresponds to
the \uwds server performing $n \times m$ requests to notify clients of the
update).  The space complexity is the same (as clients own a full copy of the
worlds they monitor), except for mesh data whose space and time complexities are
$O(1)$ (only the server stores the mesh data).

In the common case of one client performing a full update of a single world
(with $p$ nodes) at each time step, the complexity of propagating these changes across
the network would be $O(p \times m)$.
